Pre/Post-Trikafta

### 2022-01-19 Christine Chan/Pre-post Trikafta/pre_post_trikafta.Rmd
Update pre_post_trikafta.Rmd

analytic_cm <- rbind(reg_tab1 , analytic_montana1,analytic_wash1,analytic_uofm3 )

@@

tab3 <- tableby(time~ average_sensor
                + min_sensor
                + max_sensor
                + percent_time_over_120
                + percent_time_over_140
                + percent_time_over_200
                + avg_excur_over_140_per_day
                + avg_excur_over_200_per_day
                + percent_time_under_60
                + percent_time_under_70
                + average_auc_per_day
                + standard_deviation
                + r_mage, data=cgm0_small, control=mycontrols)
tab3 <- tableby(~average_sensor
                + min_sensor
                + max_sensor
                + percent_time_over_120
                + percent_time_over_140
                + percent_time_over_200
                + avg_excur_over_140_per_day
                + avg_excur_over_200_per_day
                + percent_time_under_60
                + percent_time_under_70
                + average_auc_per_day
                + standard_deviation
                + r_mage, data=cgm0[cgm0$time == "post",]
                , control=mycontrols)

@@

tab1 <- tableby(~age+bmipct + Weight + Sex + ppFEV1 + ppFVC  +
                  G.tube.in.past.12.months + Pancreatic.Status +
                  genoRisk + location+BMI.Value + age_category, 
                data=analytic_cm[analytic_cm$CFF.ID %in% cgm0_small$ID,])
summary(tab1)
```

>>>>

analytic_cm <- rbind(reg_tab1 , analytic_montana1,analytic_wash1,analytic_uofm3 )
# Add BMI category
analytic_cm$bmicat = reg3_BMI$bmicat[match(analytic_cm$CFF.ID,reg3_BMI$CFF.ID)]

@@

tab3a <- tableby(time~ average_sensor
                + min_sensor
                + max_sensor
                + percent_time_over_120
                + percent_time_over_140
                + percent_time_over_200
                + avg_excur_over_140_per_day
                + avg_excur_over_200_per_day
                + percent_time_under_60
                + percent_time_under_70
                + average_auc_per_day
                + standard_deviation
                + r_mage, data=cgm0_small, control=mycontrols)
tab3c <- tableby(~average_sensor
                + min_sensor
                + max_sensor
                + percent_time_over_120
                + percent_time_over_140
                + percent_time_over_200
                + avg_excur_over_140_per_day
                + avg_excur_over_200_per_day
                + percent_time_under_60
                + percent_time_under_70
                + average_auc_per_day
                + standard_deviation
                + r_mage, data=cgm0[cgm0$time == "post",]
                , control=mycontrols)

@@

tab3b <- tableby(~age+bmipct + Weight + Sex + ppFEV1 + ppFVC  +
                  G.tube.in.past.12.months + Pancreatic.Status +
                  genoRisk + location+BMI.Value + age_category, 
                data=analytic_cm[analytic_cm$CFF.ID %in% cgm0_small$ID,])
summary(tab3a)
summary(tab3b)
summary(tab3c)
```
